Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-04-23 outputs/paper/paper.Rmd
result session writing done

Last is the unchanged group:  Figure \@ref(fig:fig3), Figure \@ref(fig:fig5), Figure \@ref(fig:fig7), Figure \@ref(fig:fig8), Figure \@ref(fig:fig9), Figure \@ref(fig:fig12), Figure \@ref(fig:fig13), Figure \@ref(fig:fig15), Figure \@ref(fig:fig16) and Figure \@ref(fig:fig17).
This group can be interpreted as a group that is absolutely essential in society. For instance, no matter what we face, education 
1. Essential
2. Indifference regarding the virus.

@@

>>>>

3) Unchanged: Childcare, Crime rates, Education, Energy, Environment, Mass Transportation, Park and recreation, Roads, Scientific research, Social security
Last is the unchanged group:  Figure \@ref(fig:fig3), Figure \@ref(fig:fig5), Figure \@ref(fig:fig7), Figure \@ref(fig:fig8), Figure \@ref(fig:fig9), Figure \@ref(fig:fig12), Figure \@ref(fig:fig13), Figure \@ref(fig:fig15), Figure \@ref(fig:fig16) and Figure \@ref(fig:fig17).
This group can be interpreted as a group that is absolutely essential in society regardless the virus. For instance, no matter what we face, education must go on. In a same sense, other variables must go on regardless the virus. One thing to notice here is the outdoor services such as mass transportation, park or roads. One of major changes before and after the pandemic is virtual life. Many facilities ran virtually, so I assumed that national spending on outdoor services would belong to the negative group. However, it turned out to be unchanged. This means that they jumped clear of the pandemic.

@@

## what is something that we learn about the world?
